Spatial Reasoning and Statistical Graphics

### 2014-10-22 Paper/Draft1/TestingVisualAptitude.Rnw
ETS Version

\comment{could we also refer to the fact that these tests have been long established (maybe with references to earlier tests or updates?) \textit{Yes, definitely. I'll pull up some references for that too...}}
The advantage of using tests from the Kit of Factor Referenced Cognitive tests \citep{ekstrom1976manual} is that the tests are extremely well studied \citep{voyer1995magnitude,schaie1998longitudinal,hampson1990variations,mayer1994whom} and comparison data are available from the validation of these factors.
\comment{the well studied reference list needs to be a bit more extensive ... do you know this book by Michel Hersen?\\\textit{I was working on it yesterday along with trying to validate the general idea that reading graphics requires certain spatial abilities. It's definitely a work in progress. I haven't seen that book before, but I'm not at all surprised it exists.}}

>>>>

\comment{could we also refer to the fact that these tests have been long established (maybe with references to earlier tests or updates?) \textit{Yes, definitely. I'll pull up some references for that too...}}
The advantage of using tests from the Kit of Factor Referenced Cognitive tests \citep{ekstrom1976manual} is that the tests are extremely well studied (including an extensive meta-analysis by \citet{voyer1995magnitude} of the spatial tests we are using in this study) and comparison data are available from the validation of these factors \citep{schaie1998longitudinal,hampson1990variations,mayer1994whom} and previous versions of the kit \citep{educational1963kit}.
\comment{the well studied reference list needs to be a bit more extensive ... do you know this book by Michel Hersen?\\\textit{I was working on it yesterday along with trying to validate the general idea that reading graphics requires certain spatial abilities. It's definitely a work in progress. I haven't seen that book before, but I'm not at all surprised it exists.}}
